---
output: pdf_document
---

```{r, echo=F, warning=F, message=F}
library(ggplot2)
library(dplyr)
library(tidyr)

library(pracma)
library(cowplot)
library(latex2exp)
library(R.matlab)
library(zoo)
library(viridis)

source('config.R')
```

```{r, echo=F}
folder_name <- 'capstone'
should_save <- F
jaws_color <- 'orange'
zorin_color <- 'purple'

load_mat <- function(name, folder_name='capstone', convert=T) {
  d <- readMat(file.path(data_dir, folder_name, paste(name, '.mat', sep = '')))
  if (convert)  d[['x']] <- as.matrix(as.numeric(d[['x']])) # make x a column vector
  d
}

std_dev_plot_from_mat <- function(name, ...) {
  d <- load_mat(name)
  x <-  d[['x']]
  y <- d[['y']]
  std_err <- d[['std.err']]
  std_dev_plot(x, y, std_err, ...)
}

std_dev_plot_from_mat_monkeys <- function(name, ...) {
  jaws <- load_mat(paste0(name, '_jaws'))
  zorin <- load_mat(paste0(name, '_zorin'))
  x <-  cbind(jaws$x, zorin$x)
  y <- cbind(jaws$y, zorin$y)
  std_err <- cbind(jaws$std.err, zorin$std.err)
  std_dev_plot_monkeys(x, y, std_err, ...)
}

std_dev_plot <- function(x, y, std_err, color = 'blue', legend_labels=NULL) {
  n <- dim(y)[2]
  if (n > 1 & length(color) != n) {
      colors <- matlab::fliplr(matlab::jet.colors(n))
  } else {
    colors <- color
  }
  means <- data.frame(x=x, y=y)
  colnames(means) <- c('x', 1:n)
  stds <- data.frame(x=x, std_err=std_err)
  colnames(stds) <- c('x', 1:n)
  p <- means %>% 
    gather('name', y, -x) %>%
    left_join(stds %>% gather('name', std_err, -x), by = c('x', 'name')) %>%
    ggplot(aes(x = x)) +
    geom_line(aes(y = y, col = name), size=1) +
    geom_ribbon(aes(ymin = y-std_err, ymax = y+std_err, fill = name), alpha=0.2) +
    scale_color_manual(labels=legend_labels, name = NULL, values = colors) +
    scale_fill_manual(values = colors) +
    guides(fill=F) +
    theme_classic() +
    theme(text = element_text(size=16))
  if (is.null(legend_labels)) p <- p + guides(color = F)
  p
}

std_dev_plot_monkeys <- function(x, y, std_err, colors = c(jaws_color, zorin_color)) {
  n <- dim(x)[1]
  assertthat::are_equal(dim(x)[2], 2)
  assertthat::are_equal(dim(y)[2], 2)
  assertthat::are_equal(dim(std_err)[2], 2)
  jaws <- data.frame(x=x[,1], y=y[,1], std_err=std_err[,1], name="J")
  zorin <- data.frame(x=x[,2], y=y[,2], std_err=std_err[,2], name="Z")
  rbind(jaws, zorin) %>%
    ggplot(aes(x=x)) +
    geom_line(aes(y = y, col = name), size=1) +
    geom_ribbon(aes(ymin = y-std_err, ymax = y+std_err, fill = name), alpha=0.2) +
    scale_color_manual(name = NULL, values = colors) +
    scale_fill_manual(values = colors) +
    guides(fill=F) +
    theme_classic() +
    theme(text = element_text(size=16))
}
```


```{r, fig.cap="Figure 1: Data summary.", echo=F}
spike_train_lfp_trials <- function(times, spikes, lfp, vjust=0) {
  s <- zeros(length(times), length(spikes))
  for (i in 1:size(s,2)) {
    s[spikes[[i]][[1]],i] <- 1
  }
  d <- data.frame(x=times, y=s, lfp=lfp) %>%
    gather('unit', 'fired', -x, -lfp) 
  l <- 1:size(s,2)
  names(l) <- levels(as.factor(d$unit))
  d$unit <- as.numeric(l[d$unit]) + vjust
  d %>% 
    ggplot(aes(x = x / 1000)) + 
    geom_tile(aes(y = unit, fill = as.factor(fired)), height = 0.8) +
    geom_line(aes(y = interp1(range(lfp), c(0,0.9*vjust), lfp)), size=0.5) +
    expand_limits(y = 0) +
    scale_fill_manual(values = c('white', 'black')) +
    guides(fill = F) +
    theme_classic() +
    theme(axis.title.y = element_blank(),
          axis.text.y = element_blank(), 
          axis.ticks.y = element_blank()) +
    labs(x = 'Time (s)')
}

trial <- load_mat('1_a_trial')$trial
lfp <- load_mat('1_a_lfp')$y
spikes <- load_mat('1_a_spikes')

# this is necessary because ggplot has a bug
plot_a <- spike_train_lfp_trials(spikes$x, spikes$y, lfp, vjust=10) + 
  geom_vline(xintercept = c(1.880,2.614,2.831,3.040), color = c('red', 'green', 'blue', 'purple'))

trial <- load_mat('1_b_trial')$trial
lfp <- load_mat('1_b_lfp')$y
spikes <- load_mat('1_b_spikes')

plot_b <- spike_train_lfp_trials(spikes$x, spikes$y, lfp, vjust=10) + 
  geom_vline(xintercept = c(0.658, 1.653, 1.693), color = c('red', 'green', 'blue'))

jaws <- data.frame(rates = t(load_mat('1_c_jaws')$rates), name = 'J')
zorin <- data.frame(rates = t(load_mat('1_c_jaws')$rates), name = 'Z')
#d <- rbind(jaws, zorin)
d <- jaws
# can't use geom_density since it has an unsightly bottom line
plot_c <- d %>%
  ggplot(aes(rates, col=name)) + 
  stat_density(geom='line', bw = 2, position = 'identity') +
  expand_limits(x = max(d$rates)*1.1) +
  #scale_color_manual(values = c('orange', 'blue'), name = NULL) +
  scale_color_manual(values = c("orange"), name = NULL) +
  labs(x = "Firing Rates (Hz)", y = "Density") +
  theme_classic() +
  theme(legend.position = c(0.98,0.98),
        legend.justification = c('right', 'top'))

jaws <- data.frame(rxn_time = t(load_mat('1_d_jaws')$rxn.time), name = 'J')
zorin <- data.frame(rxn_time = load_mat('1_d_zorin')$rxn.time, name = 'Z')
d <- rbind(jaws, zorin)
plot_d <- d %>%
  ggplot(aes(x=rxn_time, col=name)) +
  stat_density(geom='line', bw = 10, position = 'identity') +
  expand_limits(x = max(d$rxn_time)*1.1) +
  scale_color_manual(values = c('Z'=zorin_color, 'J'=jaws_color), name = NULL) +
  labs(x = "Reaction Time (ms)", y = "Density") +
  theme_classic() +
  theme(legend.position = c(0.98,0.98),
        legend.justification = c('right', 'top'))

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO', label_x = c(0.05, 0.05, 0, 0))

if (should_save) ggsave(file.path(plot_save_dir, folder_name, '1.png'), p) else print(p)
```
A) Successful trial. Red = fixation, green = noise onset, blue = shape onset, purple = saccade. B) Failure to detect shape. C) Firing rate distribution. D) Reaction time distribution.

Figure 2 should probably be some information analysis plots. 

```{r, fig.cap="Figure 3: Relevant LFP frequencies.", echo=F}
plot_a <- std_dev_plot_from_mat('3_a_jaws', 
                      color = c('red', 'green', 'blue'), 
                      legend_labels = c("Low", "Medium", "High")) +
  labs(x = "Frequency (Hz)", y = "Success Rate") +
  theme(legend.position = c(0.01,1),
        legend.justification = c('left', 'top'))

n_bins <- 60
breaks <- seq(0, 360, length.out = n_bins+1)
phases <- lapply(load_mat('3_b_jaws',convert = F)$x, function(x) x[[1]])
phases <- lapply(phases, function(x) rad2deg(x) %% 360)
phases <- vapply(phases, function(x) table(cut(x, breaks = breaks)) / length(x), numeric(n_bins))
phases <- data.frame(phases)
colnames(phases) <- 1:6
plot_b <- phases %>%
  mutate(x = rollmean(seq(0, 360, length.out = n()+1), 2)) %>%
  gather(num, y, -x) %>%
  mutate(num = as.numeric(num),
         success = ifelse(num %% 2 == 1, 'yes', 'no'),
         f = rep(c("Alpha", "Beta", "Gamma"), each=2)[num]) %>%
  select(-num) %>%
  group_by(f) %>%
  spread(success, y) %>%
  mutate(rate = yes / (yes+no)) %>%
  ggplot(aes(x = x, y=rate)) +
  geom_line(col='#0000FF') +
  coord_polar() +
  facet_wrap(~ f) +
  theme(panel.grid.major.y = element_line(size = 0.5, color = 'darkgrey'),
        axis.ticks.y = element_blank(),
        panel.spacing = unit(0.2, 'cm')) +
  scale_x_continuous(name = NULL,  breaks=NULL) +
  scale_y_continuous(name = NULL, labels = NULL)


d <- load_mat('3_c_jaws')
dist_bins <- d[['dist.bins']]
legend_labels <- c()
for (i in 1:dim(dist_bins)[2]) {
  legend_labels[i] <- TeX(sprintf('%.0f - %.0f $\\mu m$', dist_bins[1,i], dist_bins[2,i]))
}

plot_c <- std_dev_plot(d$x, d$y, d$std.err, legend_labels = legend_labels) +
  xlab('Frequency (Hz)') + ylab('Coherence') + 
  theme(legend.text = element_text(size=12), 
        legend.position = c(0.98,0.98),
        legend.justification = c('right', 'top'),
        legend.key.size = unit(0.1, units = 'in'))

plot_d <- std_dev_plot_from_mat('3_d_jaws', legend_labels=c("Success", "Failure")) +
  labs(x = "Frequency (Hz)", y = TeX("$\\sigma$ Coherence")) +
  theme(legend.position = c(0.98,0.98),
        legend.justification = c('right', 'top'))

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels="AUTO", label_size = 20)

if (should_save) {
  ggsave(file.path(plot_save_dir, folder_name, '3.png'), p, 
                        height = 10, width = 10, units = 'in') 
} else print(p)
```
A) Normalied success rate (% success / (% success + % failure) so that null = 50%) vs frequency for trials with high, medium, and low LFP power at the given frequency. B) Normalized success rate vs phase in high LFP power trials (blue line from (A)). C) Coherence binned by interelectrode distance. D) Value for $\sigma$ of a Gaussian fitted to coherence vs distance for each frequency.  

```{r, fig.cap="Figure 4: Spike-triggered averages.", echo=F}
plot_sta <- function(letter) {
  std_dev_plot_from_mat(sprintf('4_%s_jaws', letter)) +
    labs(x="Time (s)", y = "") +
    theme(text = element_text(size=12))
}

plot_a <- plot_sta('a') # success, alpha
plot_b <- plot_sta('b') # failure, alpha
plot_c <- plot_sta('c') # success, gamma
plot_d <- plot_sta('d') # failure, gamma

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO', ncol = 2)

if (should_save) ggsave(file.path(plot_save_dir, folder_name, '4.png'), p) else print(p)
```
Spike-triggered averages averaged over all recorded neurons and trials fitting the given condition:
Columns: Success (left), failure (right)
Rows: High alpha power trials (top), high gamma power trials (bottom)

```{r, fig.cap="Figure 5: Phase locking.", echo=F}
plot_ppc <- function(letter) {
  std_dev_plot_from_mat(sprintf('5_%s_jaws', letter)) +
    labs(x="Frequency (Hz)", y = "PPC") +
    theme(text = element_text(size=12))
}

plot_a <- plot_ppc('a') # success, alpha
plot_b <- plot_ppc('b') # failure, alpha
plot_c <- plot_ppc('c') # success, gamma
plot_d <- plot_ppc('d') # failure, gamma

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO', ncol = 2)

if (should_save) ggsave(file.path(plot_save_dir, folder_name, '5.png'), p) else print(p)
```
Average pairwise phase consistency averaged over all recorded neurons and trials fitting the given condition:
Columns: Success (left), failure (right)
Rows: High alpha power trials (top), high gamma power trials (bottom)

```{r, fig.cap="Figure 6: Learning.", echo=F}
plot_heatmap <- function(name, freq_cutoff=100) {
  d <- load_mat(name, convert = F)
  days <- as.Date(unlist(lapply(d$x, function(x) x[[1]])))
  freqs <- d$freqs
  vals <- d$y
  expand.grid(f=freqs, trial=1:length(days)) %>%
    mutate(z = as.numeric(vals),
           z = ifelse(is.infinite(z), NaN, z)) %>%
    filter(f <= freq_cutoff) %>%
    ggplot(aes(trial, f)) +
    geom_raster(aes(fill=z)) +
    scale_fill_gradientn(colors = inferno(1000), name = NULL) +
    labs(x = "Day number", y = "Frequency")
}

d <- load_mat('6_a_jaws', convert = F)
days <- as.Date(unlist(lapply(d$x, function(x) x[[1]])))
rate <- d$y
plot_a <- data.frame(y=rate) %>%
  mutate(x = 1:n()) %>%
  ggplot(aes(x=x, y=y)) +
  geom_line() +
  labs(x = "Trial number", y = "Success Rate")

plot_b <- plot_heatmap('6_b_jaws')
plot_c <- plot_heatmap('6_c_jaws')
plot_d <- plot_heatmap('6_d_jaws')

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO')

if (should_save) ggsave(file.path(plot_save_dir, folder_name, '6.png'), p) else print(p)
```
A) Success rate vs trial number. B) Spatial distribution of coherence (the $\sigma$ from figure 3D) for each day. C) PPC (averaged over all neurons and all trials). D) Standard deviation of PPC among neurons in all trials in a given day.

Maybe some neurons learn by increasing their deviation from the alpha rhythm, but there aren't a lot of units later, so it's difficult to say anything definitively with either of (C) or (D).

```{r}
plot_a <- plot_heatmap('coh_noise_day_jaws') +
  ggtitle('Postnoise, Jaws')
plot_b <- plot_heatmap('coh_noise_day_zorin') +
  ggtitle('Postnoise, Zorin')
plot_c <- plot_heatmap('coh_shape_day_jaws') +
  ggtitle('Preshape, Jaws')
plot_d <- plot_heatmap('coh_shape_day_zorin') +
  ggtitle('Preshape, Zorin')

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO')

if (should_save) ggsave(file.path(plot_save_dir, folder_name, 'spatial_coh.png'), p) else print(p)
```

```{r, fig.cap="Far coherences at 15 Hz versus time"}
d <- load_mat('far_coh_shape_day_zorin', convert = F)
plot_a <- std_dev_plot(1:length(d$x), t(d$y), t(d$std.err)) + 
  labs(x = "Day number", y = "Coherence") + 
  ggtitle("~4-5 mm, 15 Hz, Zorin")

d <- load_mat('far_coh_shape_day_jaws', convert = F)
plot_b <- std_dev_plot(1:length(d$x), t(d$y), t(d$std.err)) + 
  labs(x = "Day number", y = "Coherence") + 
  ggtitle("~4-5 mm, 15 Hz, Jaws")

p <- plot_grid(plot_a, plot_b, labels='AUTO')

if (should_save) ggsave(file.path(plot_save_dir, folder_name, 'far_spatial_coh_15.png'), p, width = 10, units = 'in') else print(p)
```


```{r, fig.cap="Success rate by phase split by low / high frequency"}
plot_low_high_phase_hist <- function(name) {
  n_bins <- 60
  breaks <- seq(0, 360, length.out = n_bins+1)
  phases <- lapply(load_mat(name, convert = F)$x, function(x) x[[1]])
  phases <- lapply(phases, function(x) rad2deg(x) %% 360)
  phases <- vapply(phases, function(x) table(cut(x, breaks = breaks)) / length(x), numeric(n_bins))
  phases <- data.frame(phases)
  colnames(phases) <- 1:4
  freq_names <- rep(c("Low (7.5-25 Hz)", "High (31-100 Hz)"), each=2)
  freq_names <- factor(freq_names, levels=freq_names[c(1,3)])
  phases <- phases %>%
    mutate(x = rollmean(seq(0, 360, length.out = n()+1), 2)) %>%
    gather(num, y, -x) %>%
    mutate(num = as.numeric(num),
           success = ifelse(num %% 2 == 1, 'yes', 'no'),
           f = freq_names[num]) %>%
    select(-num) %>%
    group_by(f) %>%
    spread(success, y) %>%
    mutate(rate = yes / (yes+no))
  phase_means <- phases %>%
    group_by(f) %>%
    summarize(v = mean(rate*exp(1i*deg2rad(x)))) %>%
    mutate(x = rad2deg(Arg(v)) %% 360,
           xend = x,
           y = 0,
           yend = Mod(v))
  phases %>%
    ggplot(aes(x = x, y=rate)) +
    geom_polygon(fill=NA, col='#0000FF') +
    geom_segment(data = phase_means, aes(x=x, y=y, xend=xend, yend=yend), inherit.aes = F, size=0.5, col='darkgrey') +
    coord_polar() +
    facet_wrap(~ f) +
    theme(panel.grid.major.y = element_line(size = 0.5, color = 'darkgrey'),
          axis.ticks.y = element_blank(),
          panel.spacing = unit(0.2, 'cm')) +
    scale_x_continuous(name = NULL,  breaks=NULL) +
    scale_y_continuous(name = NULL, labels = NULL)
}

plot_a <- plot_low_high_phase_hist('bigger_bins_phases_zorin') +
  ggtitle("Jaws")
plot_b <- plot_low_high_phase_hist('bigger_bins_phases_jaws') +
  ggtitle("Zorin")

p <- plot_grid(plot_a, plot_b, labels='AUTO', nrow=2)

if (should_save) ggsave(file.path(plot_save_dir, folder_name, 'low_high_phase_hist.png'), p, width = 3, units = 'in') else print(p)
```

```{r, fig.cap="Reaction times versus (normalized) preshape LFP power"}
make_rxn_time_pow_bin_df <- function(name) {
  mat <- load_mat(paste0('rxn_time_pow_bin_', name), convert = F)
  pow_lab <- as.factor(mat$x)
  freq_lab <- as.factor(c("Low (7.5-25 Hz)", "High Frequency (31-100 Hz)"))
  levels(freq_lab) <- freq_lab
  freqs <- lapply(mat$y, function(x) 
                            lapply(x[[1]], function(y) y[[1]]))
  d <- data.frame(y = numeric(0), pow_lab = numeric(0), freq_lab = numeric(0))
  for (i in 1:length(freqs)) {
    for (j in 1:length(freqs[[i]])) {
      e <- data.frame(y = freqs[[i]][[j]], pow_lab = pow_lab[j], freq_lab = freq_lab[i])
      d <- rbind(d, e)
    }
  }
  return(d)
}
zorin <- make_rxn_time_pow_bin_df('zorin') %>%
  mutate(name = 'Z')
jaws <- make_rxn_time_pow_bin_df('jaws') %>%
  mutate(name = 'J')
rbind(zorin, jaws) %>%
  ggplot(aes(x=pow_lab, y=y)) +
  geom_boxplot(aes(col=name)) +
  scale_color_manual(values = c('Z'=zorin_color, 'J'=jaws_color)) +
  guides(col = F) +
  facet_grid(name~freq_lab) +
  labs(y = "Reaction Time (ms)", x = "Power bin")
```

```{r, fig.cap="Coherence at 20 Hz Across Trials"}
make_trial_coh_df <- function(name, analysis_type) {
  mat <- load_mat(sprintf('trial_coh_%s_%s', analysis_type, name))
  data.frame(x = mat$x, y = mat$y, std_err = mat$std.err, name=name, type=analysis_type)
}
x_lab <- "Trial Index"
y_lab <- "Coherence"
plot_a <- std_dev_plot_from_mat('trial_coh_noise_jaws') +
  labs(x = x_lab, y = y_lab, title = "Postnoise Jaws")

plot_b <- std_dev_plot_from_mat('trial_coh_shape_jaws') +
  labs(x = x_lab, y = y_lab, title = "Preshape Jaws")

plot_c <- std_dev_plot_from_mat('trial_coh_noise_zorin') +
  labs(x = x_lab, y = y_lab, title = "Postnoise Zorin")

plot_d <- std_dev_plot_from_mat('trial_coh_shape_zorin') +
  labs(x = x_lab, y = y_lab, title = "Preshape Zorin")

d_a <- make_trial_coh_df('jaws', 'noise')
d_b <- make_trial_coh_df('jaws', 'shape')
d_c <- make_trial_coh_df('zorin', 'noise')
d_d <- make_trial_coh_df('zorin', 'shape')
rbind(d_a, d_b, d_c, d_d) %>%
  ggplot(aes(x=x, y=y)) +
  geom_line(col = 'blue') +
  geom_ribbon(aes(ymin = y-std_err, ymax = y+std_err), alpha=0.2, fill='blue') +
  guides(fill=F) +
  facet_grid(name ~ type)
  

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO', nrow=2)

if (should_save) ggsave(file.path(plot_save_dir, folder_name, 'trial_coh_shape.png'), p, width = 4, units = 'in') else print(p)
```

```{r, fig.cap="Success rate"}
make_success_rate_df <- function(name) {
  mat <- load_mat(sprintf('success_rate_coh_noise_%s', name))
  data.frame(x = mat$x, y = mat$y, name=as.character(c('jaws'='J', 'zorin'='Z')[name]))
}

plot_success_rate <- function(name) {
  d <- make_success_rate_df(name)
  std_dev_plot(as.matrix(d$x), as.matrix(d$y), as.matrix(rep(0,nrow(d))))
}

plot_a <- plot_success_rate('zorin') + 
  labs(x = "Trial Index", y = "Sucess rate", title = "Zorin")
plot_b <- plot_success_rate('jaws') + 
  labs(x = "Trial Index", y = "Sucess rate", title = "Jaws")
plot_c <- std_dev_plot_from_mat('trial_coh_noise_zorin') +
  labs(x = "Trial Index", y = "Coherence")
plot_d <- std_dev_plot_from_mat('trial_coh_noise_jaws') +
  labs(x = "Trial Index", y = "Coherence")

p <- plot_grid(plot_a, plot_b, plot_c, plot_d, labels='AUTO', nrow=2)

if (should_save) ggsave(file.path(plot_save_dir, folder_name, 'trial_coh_shape.png'), p, width = 4, units = 'in') else print(p)
```

