```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

source('config.R')
```

## t-SNE Electrode Embedding
This is just a t-SNE embedding of the mean condition traces for each electrode.
TODO: Look at embedding of the mean LFP at each instance of a condition (how much do conditions vary?)
```{r}
d <- read.csv(file.path(data_dir, 'tsne.csv'))
d %>% ggplot(aes(x,y,color=labels,label=electrode_num)) +
    geom_text() +
    theme_minimal() +
    ggsave(file.path(plot_save_dir, 'tsne_plot_r.png'))
```

## Reaction Times and LFP Slope
Checking to see if the slope of the mean LFP signal ranging from 200 ms prior to a shape stimulus to the saccade is correlated with the reaction time (the time between the shape and saccade).
```{r}
d <- read.csv(file.path(data_dir, 'slope_data.csv'))
colnames(d) <- c('slopes', 'rxn_times')
mod <- lm(rxn_times ~ slopes, d)
summary(mod)
ggplot(d, aes(slopes, rxn_times)) + 
  geom_point() +
  theme_minimal()
```

So, not much to be seen here...


